---
title: "General Social Survey"
author: "Jonathan Urbano"
date: "March 12, 2024"
output: 
  html_document:
    number_sections: true
    toc: true
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(foreign)
source("GrabData.R")
```





#  Question 2

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

Is there a difference in years of education (EDUC) between the those who did or did not vote in 2012 (VOTE16)?

## Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

I looked at the data and it had a numerical variable which was education and had a factor variable which was VOTE16 so the Numerical~Cat/rmd helper file was used 



##Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

### Descriptive Results

#### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
plot(EDUC~VOTE16,data=GSSdata)
```

Looking at the median, people who voted have a median of 15 years of education and people who didn't vote have a median of 13 years of education

#### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(EDUC~VOTE16,data=GSSdata)
```

Viewing the numerical results, it can be observed that people who voted have a higher education level of 15.625 years and those that didn't vote have a lower average education level at 13.7 years. 128 people in total voted and the 50 people that didn't vote, showing that people that tend to vote more have a higher level of education.

### Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(EDUC~VOTE16,data=GSSdata)
```

The inferential results have given us a low p-value which is the statistical evidence between the voters and the non-voters. We can see the mean education level that voted in the group that voted is 15.625 and the mean education level in the group of people that didn't vote is 13.680

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
